\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{float}
\usepackage{hyperref}

\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=blue,
    urlcolor=blue
}
\begin{document}
%\selectlanguage{english}
\pagenumbering{Roman}



\title{\begin{Huge}
\textbf{Software Requirements Specification: Simulation Platform for Smart Fridge and Sudoku Solver}
\end{Huge}}
\author{\begin{Large}
Sreenivas, Jonas and Mariusz
\end{Large}}
\date{\today}
\maketitle
\thispagestyle{empty}
\begin{center}
\begin{large}
\textbf{Version:} 1.0
\\  \textbf{Based on:} IEEE SRS Template
\end{large}
\end{center}
\newpage
\tableofcontents \newpage
\pagenumbering{arabic}
\section{Introduction}
\subsection{Purpose}
This document is a software requirement specification for the software platform which is built to aid the SmartFridge and Sudoku solver projects by providing simulated data.
\subsection{Document Conventions}
\begin{itemize}
\item Links are marked in blue color and are accessible through the web browser.
\item Reference titles are in italics for easier viewing
\end{itemize}
\subsection{Intended Audience and Reading Suggestions}
The document is intended for the Systems and Software Engineering lecture (WS 2017-18) at Goethe University. This document is also developers and document writers of our related projects: SmartFridge and sudoku solver. The document must be read fully in order and it is preferred to read through the documents of the related projects to get better understanding.
\subsection{Product Scope}
A software platform for generating images which could be used as a dataset for other projects. For understanding scope of other projects, please refer to smart fridge software requirements specification document.
\subsection{References}
\begin{itemize}
\item IEEE, \textit{Software Requirements Specification}. Available at \url{https://view.officeapps.live.com/op/view.aspx?src=https://web.cs.dal.ca/~hawkey/3130/srs_template-ieee.doc}
\item Stuart R. Faulk, \textit{Software Requirements: A Tutorial}, 1995. Available at \url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.198.7770&rep=rep1&type=pdf}
\end{itemize}
\newpage
\section{Overall Description}
\subsection{Product Perspective}
\subsection{Product Functions}
\subsection{User Classes and Characteristics}
\subsection{Operating Environment}
\subsection{Design and Implementation Constraints}
\subsection{User Documentation}
\subsection{Assumption and Dependencies}
\newpage
\section{External Interface Requirements}
\subsection{User Interfaces}
\subsection{Hardware Interfaces}
\subsection{Software Interfaces}
\subsection{Communications Interfaces}
\newpage
\section{System Features}
\subsection{Feature 1}
\subsection{Feature 2}
\section{Other Nonfunctional Requirements}
\subsection{Performance Requirements}
\subsection{Safety Requirements}
\subsection{Security Requirements}
\subsection{Software Quality Attributes}
\subsection{Business Rules}
\newpage
\section{Other Requirements}
\end{document}
